Summary of the things that I learned

### 2024-09-26 100-introduction.tex
Write a conclusion

The $ \lambda $-calculus is an abstract tool that is used in an area where mathematics meets computer science, to study algorithms, programming languages and even category theory. It was conceived by Alonzo Church, primarily as a foundation for mathematics instead of set theory or type theory (\autocite{church-lambda-calculus}). A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such a function could not exist (\autocite{church-number-theory}). A year later, Alan Turing showed, using previous work of Kleene (\autocite{kleene-lambda}), that a function is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine (\autocite{turing-lambda}), solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.

>>>>

The $ \lambda $-calculus is an abstract tool that is used in an area where mathematics meets computer science, to study algorithms, programming languages and even category theory. It was conceived by Alonzo Church, primarily as a foundation for mathematics instead of set theory or type theory (\autocite{church-lambda-calculus}). A couple of years later, Church used it to show that the `Entscheidungsproblem' was unsolvable: the problem asked for an algorithm that could tell about any mathematical statement whether it was true or false, and Church showed that such an algorithm could not exist (\autocite{church-number-theory}). A year later, Alan Turing showed, using previous work of Kleene (\autocite{kleene-lambda}), that an algorithm is definable using the $ \lambda $-calculus if and only if it is definable using a Turing machine (\autocite{turing-lambda}), solidifying the position of both the $ \lambda $-calculus and Turing machines as abstract models for algorithmic computation.
